Troubleshooting tau2

### 2019-05-16 code/troubleshooting_tau2.rmd
in explore. took the sqrt in the tables to make comparable to figure 1

---
title: "Troubleshooting tau2"
author: "Anton Olsson Collentine"
date: "7 mei 2019"
output: pdf_document
---

@@

* First figure: replicate panel 2 but with untruncated
* Hopefully the last 3 points will move up
* Also compare mu for truncated and untruncated versions
* Maybe see if can figure out contribution of each lab to overall effect size mu

@@

**Compare the actual values**
```{r, cache = TRUE, echo = TRUE}
b %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)

@@

res4 %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)
```
**Exactly the same result for non-truncated effects, so that seems to be the case**

**Check which effects get truncated:**

>>>>

---
title: "Troubleshooting tau2"
author: "Anton Olsson Collentine"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

@@

* First figure: replicate panel 2 but with untruncated [done]
* Hopefully the last 3 points will move up [nope :(]
* Also compare mu for truncated and untruncated versions [done]
* Maybe see if can figure out contribution of each lab to overall effect size mu [dunno]

@@

**Compare the actual values**
```{r, cache = TRUE}
b %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
  rename(trunc_ES = r.x, trunc_tau = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau = tau2.y, nontrunc_I2 = I2.y) %>% 
  mutate(trunc_tau = sqrt(trunc_tau), nontrunc_tau = sqrt(nontrunc_tau)) %>% 
  knitr::kable(booktabs = TRUE)

@@

res4 %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
  rename(trunc_ES = r.x, trunc_tau = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau = tau2.y, nontrunc_I2 = I2.y) %>% 
  mutate(trunc_tau = sqrt(trunc_tau), nontrunc_tau = sqrt(nontrunc_tau)) %>% 
  knitr::kable(booktabs = TRUE) 
```
Exactly the same result for non-truncated effects, so that seems to be the case

Let's take a closer look at the truncated vs. untruncated variance estimates for Anchoring 4 which has the largest change in I2.

```{r, cache = TRUE}
anch4 <- dat %>%
  filter(effect == "Anchoring 4 - Babies") %>% 
  rowwise() %>% 
  do(transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) 
#See this stackoverflow question to understand the usage of rowwise and 'do'
#https://stackoverflow.com/questions/22240816/dplyr-summarise-with-multiple-return-values-from-a-single-function

anch4_trunc <- anch4 %>% 
  do(transform_d_to_r(.$d, .$n1, .$n2))

anch4_nontrunc <- anch4 %>% 
  do(untruncated_d_to_r(.$d, .$n1, .$n2))

bind_cols(anch4_trunc, anch4_nontrunc) %>% 
  rename(trunc_vi = vi, nontrunc_vi = vi1) %>% 
  select(r, trunc_vi, nontrunc_vi, n) %>% 
  arrange(desc(r)) %>% 
  knitr::kable(booktabs = TRUE)

```
Note that the (biserial) r itself is not truncated and so the same between the two. It is clear truncation leads to a larger estimate of the variance for an effect.

**To summarize: Truncation leads to an increase in estimated study variance, but a (small) decrease in meta-analytic effect size estimate. In other words, truncation (as seen in the first figure) leads to a lower I2 but does not affect the $\tau$ particularly**

##Old stuff

Check which effects get truncated:
